%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Pierre}{Rouveyrol}
\title{IT, Infosec, DevOps}                               % optional, remove / comment the line if not wanted
\address{8 rue lt col Trocard}{38000}{Grenoble}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+33~634162434}                   % optional, remove / comment the line if not wanted
\email{pierre.rouveyrol@protonmail.com}                               % optional, remove / comment the line if not wanted
\homepage{https://gitlab.com/Oakenston}                         % optional, remove / comment the line if not wanted
\extrainfo{Nationality : Swiss, French}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Recruitment team}{Oryctérope Transalpin Sàrl\\Rue du Léman 18A\\1920 Martigny}
\date{January 06, 2020}
\opening{Dear Sir or Madam,}
\closing{Kind Regards,}
\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

I am writing to you today because I think that I may be a good fit for the position you are proposing as an IT/DevOps engineer in Martigny.

I was born and raised near Grenoble, France, but my family was originally from Switzerland where I intend to relocate in the very near future, most of my family still lives in VD and VS.

For the last five years, I have been working in IT with a particular emphasis on information security, which led me to learn and use automation and what a lot of people call devops since it's such a good tool for system resiliency.

I have some experience in development, firstly because it was an integral part of my studies, secondly, because for a year and a half, I worked at Inria (a public research center) developing efficient password cracking strategies.
My mission at Thales was to provide design considerations for the security of a complex cloud based SCADA project.

Finally, I spent the last three years in the IT department of a big software company. My mission was to work in close proximity to the CISO to implement the necessary evolutions in terms of security and automation of the infrastructure.
I was also the main level 3 correspondant, with some level 2 support included.

I understand that the job you offer is for level 1 support, so I think I could be qualified for this as well. I am mostly proficient with GNU/Linux oriented technologies, my Windows knowledge lagging somewhat behind.
I of course am very familiar with most networking technologies, at my previous occupation, I was often tasked to set up inter-companies VPN, installing networking infrastructure in new locations and monitoring all of it.

Since I was the main person in charge of most servers (approximately 150, running Debian on OpenStack), I am also quite used to Ansible, and somewhat competent with Kubernetes, though not to a point where I completely trust it yet.

I have to confess that I am looking for a more technical job than purely level 1 support, debugging user mistakes on excel and so on, but I am not against it being a part of the job.
\newpage
I have to say your website doesn't tell me much about what actual product your company develops, but I understand that it is fintech and as such, I believe that my Infosec background may be especially useful.

I could be available from March 2020.

If you think that I could be a good fit for your needs, please do not hesitate to call or email me.

\makeletterclosing

\end{document}


%% end of file `template.tex'.
