%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[scale=0.93]{geometry} % Reduce document margins
\usepackage[utf8]{inputenc}
\usepackage{pgfplots}

\definecolor{s1}{RGB}{56,115,179}
\renewcommand*{\namefont}{\fontsize{24}{29}\mdseries\upshape}
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name
\usepackage{xpatch}% http://ctan.org/pkg/xpatch
\xpatchcmd{\cvitem}{#3}{\footnotesize #3}{}{}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Pierre} % Your first name
\familyname{Rouveyrol} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Curriculum Vitae}
\address{La Ruelle 3}{1268 Begnins, Suisse}
\mobile{+41 79 554 78 76}
%\fax{(000) 111 1113}
\email{pierre@rouveyrol.ch}
%\homepage{https://gitlab.com/Oakenston}{https://gitlab.com/Oakenston} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
\extrainfo{Nationality : Swiss, French}
%\photo[50pt][0pt]{pictures/portrait} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
\quote{Sysadmin, Infosec, Devops, Open Source, 7 years experience}

\renewcommand*\namefont{\fontsize{25}{48}\selectfont}
\renewcommand*\sectionfont{\fontsize{14}{24}\selectfont}
\renewcommand*\subsectionfont{\fontsize{11}{24}\selectfont}
\renewcommand*\hintfont{\fontsize{10}{24}\selectfont}
\pgfplotsset{compat=1.15}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title


%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Skills}
\cvitem{\textbf{System Administration}}{
\textit{OS} : GNU/Linux, BSD, Windows. \newline
\textit{Monitoring} : Zabbix, ELK, Grafana, Splunk, Prometheus, Nagios.\newline
\textit{Orchestration} : Ansible, Puppet, Foreman, Rundeck, Kubernetes
}
\cvitem{\textbf{Virtualization}}{
KVM, QEMU, Xen, VMWare, Docker/Podman, Docker Compose, Kubernetes.
}
\cvitem{\textbf{Security}}{
Rapid7 InsightVM and InsightIDR, Azure Sentinel, Pentesting, Applied cryptography
}
\cvitem{\textbf{Network}}{
PFSense, Fortinet, DHCP, DNS, VPN: IPSec, OpenVPN and Wireguard\newline
Nginx, Apache, HAProxy
}
\cvitem{\textbf{Cloud}}{
Openstack, Kubernetes, Azure, AWS, S3, Swift, CEPH, Rook. 
}
\cvitem{\textbf{DevOps}}{
Git, CI/CD : Gitlab and Jenkins
}
\cvitem{\textbf{Development}}{
C++, Python, Bash, Java, ADA and Go. Web : Flask and Hugo. REST APIs.
}
\cvitem{\textbf{Soft skills}}{
I have been driving adoption of security products and uniformization of best practices within an IT context. I have also been managing L1 and L2 support teams, and occasionally had to recruit them. I have been giving some training regarding security best practices, cryptography and version control using Git.
}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Experience}

\cventry{05.2021-03.2022}{Systems and Automation Engineer}{\textsc{Infomaniak}}{Geneva}{Switzerland}{
Part of the team in charge of infrastructure maintenance and improvement.
\newline L4 Incident response, MCO, automation using Rundeck and Puppet.
\newline Backup automation and validation with Rundeck.
\newline SSL Certificate issuance and renewing automation, using Letsencrypt, cfssl.
\newline CI/CD pipelines development in Gitlab.
\newline Monitoring using Zabbix, Grafana, Prometheus and ELK.
\newline K8s administration, containerisation of web services for use in K8s.
\newline HA Proxy administration, load balancing, filtering, K8s ingresses.
\newline S3 administration on CEPH RADOS, Provisioning and administration of Ceph, development and maintenance of helper scripts in Python and Bash.
\newline Migration of legacy services from Xen to Open Stack or K8s.
\newline 0 downtime operations on Icecast radio clusters.
\newline Improvement of IPAM solution, with API based DHCP.
\newline Night and weekend shifts
\newline}

\cventry{03.2020-04.2021}{IT Security Specialist}{\textsc{MSC}}{Geneva}{Switzerland}{
Second in charge of EMEA security.
\newline Migration of most of the infrastructure to Azure.
\newline Architecturing of Azure services to improve security.
\newline Deployment and management of worldwide web allow listing policy. Python development of services to streamline requests related to allowlistting policy.
\newline Monitoring and incident response using Splunk, Azure Sentinel.
\newline Company wide software upgrades through GPO.
\newline Designing physical security architecture to protect videosurveillance and identification systems.
\newline Worldwide level 3 support on security related matters.
\newline Management of L2 teams in Greece, Brazil and Italy
\newline}

\cventry{01.2017-02.2020}{IT Security Specialist}{\textsc{Viseo Group}}{Grenoble}{France}{
In charge of company wide security improvement, maintenance and incident response, as well as IT operations.
\newline International level 3 IT support for Linux systems, networks and cloud infrastructure.
\newline Management of L2 teams in Morocco, Philippines and France.
\newline Introduction of Ansible to manage security controls on all servers of the company.
\newline Automation of server provisioning inside OVH's Openstack services, migration of all on prem servers to OpenStack.
\newline Automation of SSH access management using Vault for key storage and Ansible for deployment.
\newline Upgrading of all legacy web services, contributions to GLPI, Fusion Inventory.
\newline Introduction, installation and maintenance of Rapid7 InsightVM SIEM solution to manage security on servers and user terminals.
\newline Introduction and deployment of Microsoft Intune for user terminal management.
\newline Maintenance of network services using PFSense, installation and upgrade of physical and virtual instances.
\newline Setup and maintenance of IPSEC VPN links with customers using PFSense.
\newline}

\cventry{2015-2016}{Cybersecurity Engineer}{\textsc{Thales}}{Montbonnot}{France}{
Security consulting on an undisclosed SCADA project.
\newline Applying EBIOS methodology of a critical infrastructure project.
\newline Automation of SSH based access control.
\newline Pentesting monitoring, distributed and web services and Scada systems.
\newline Improvement of architecture for security.
\newline Design and implementation of security controls using Jenkins
\newline}

\cventry{2014-2015}{Research Engineer}{\textsc{Inria : Privatics}}{Montbonnot}{France}{
Research and development of a password guessing algorithm for targeted attacks based on Markov chains.
\newline Solving performance and memory constraints related to operations on huge datasets. 
\newline Several talks given about the project and its targets and implications.
\newline more details : https://team.inria.fr/privatics/omen-leveraging-personal-information-for-password-cracking/
\newline}

\cventry{03.2014-09.2014}{Research Intern}{\textsc{Inria : Privatics}}{Montbonnot}{France}{
Feasibility assessment of consumer grade Wi-Fi APs exploitation as a geotracking botnet.
\newline Reverse engineering of consumer grade internet set top boxes to evaluate the feasibility of deploying large scale, privacy threatening malware.
\newline More details : https://hal.inria.fr/hal-01151446/document
\newline}

\newpage
%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------
\vspace{4mm}
\section{Languages}
\cvitemwithcomment{French}{Native}{}
\cvitemwithcomment{English}{Fluent}{Numerous travels abroad (Irland, UK, US, Canada...) and all work in English}
\cvitemwithcomment{German}{Basic}{3 years in school}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{4mm}
\section{Education}
\subsection{Academic}
\cventry{2015-2016}{Master 2 cybersecurity}{SAFE : Sécurité, Audit, inFormatique légalE}{Université Joseph Fourier}{}{}
\cventry{2013-2014}{Master 1 computer science}{International program, MoSIG}{Université Joseph Fourier}{}{}
\cventry{2012-2013}{Bachelor computer science}{Video games conception}{Université du Québec à Chicoutimi}{}{}
\cventry{2010-2012}{DUT Informatique (French 2 year diploma)}{IUT 2 de Grenoble}{Université Pierre Mendès-France}{\textit{Rank : 10/84}}{}
\cventry{2007-2010}{Baccalauréat S-SI (Engineering)}{Lycée Ferdinand Buisson}{}{}{}
\vspace{4mm}
\subsection{MOOC}
\cventry{07.2013-09.2013}{Computer Networks}{https://www.coursera.org/}{Washington university's networks course}{\textit{Grade : 96/100}}{}
\cventry{10.2011-12.2011}{AI-Class}{https://www.ai-class.com/}{Stanford's introductory Artificial Intelligence course}{\textit{Grade : 98/100}}{}
\vspace{8mm}

%\cventry{05.2012-06.2012}{Academic internship}{\textsc{Groupe Folder}}{Voiron}{France}{
%Debugging and updating of a client support website in .NET.
%\newline Development of complex SQL queries.
%\newline Implementation and testing of new features in an ASP.NET website.
%\newline Deploy all new features in production.
%\newline}

%\vspace{8mm}
%\section{Misc Experiences}
%\cventry{2012}{UQAC}{}{Québec}{Canada}{Design and development of three video games in the context of game jams organized by Ubisoft}
%\cventry{November 2012}{Hackfest}{}{Québec}{Canada}{Participation to the CTF : http://www.hackfest.ca/en/hacking-games/friday}
%\cventry{June 2013}{Nuits du Hack}{}{Paris}{France}{Participation to OVHack and a lockpicking challenge}
%\vspace{1mm}
%\cventry{Summers}{Carpentery, Electricity meters survey, Mail sorting, Gardening}{}{}{}{}
%\cventry{Events}{Attended and gave talks, some CTF and lockpicking challenges}{}{}{}{}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------
%\section{Interests}

%\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

%\cvlistdoubleitem{Mountain sports : Paragliding, ski, hiking}{Motorcycle}
%\cvlistdoubleitem{Crafting : Blacksmithing, Electronics, DIY}{Corporate security (Tech \& Social)}
%\cvlistdoubleitem{Permaculture}{Precision Shooting}
%----------------------------------------------------------------------------------------

\end{document}
